\simname 2.0 User's Guide

### 2010-03-09 doc/manual.tex
update license text
git-svn-id: https://nocs.stanford.edu/cgi-bin/svn.cgi/booksim2.0/trunk@1535 ce7aba0d-9f81-40a6-a495-cecae84b0515
update book sim manual
git-svn-id: https://nocs.stanford.edu/cgi-bin/svn.cgi/booksim2.0/trunk@1767 ce7aba0d-9f81-40a6-a495-cecae84b0515

% Copyright (c) 2007, Trustees of Leland Stanford Junior University
% All rights reserved.
% 
% Redistribution and use in source and binary forms, with or without 
% modification, are permitted provided that the following conditions are met:
% 
% Redistributions of source code must retain the above copyright notice, this 
% list of conditions and the following disclaimer.
% Redistributions in binary form must reproduce the above copyright notice, 
% this list of conditions and the following disclaimer in the documentation 
% and/or other materials provided with the distribution.
% Neither the name of the Stanford University nor the names of its contributors
% may be used to endorse or promote products derived from this software without
% specific prior written permission.
% 
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" 
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE 
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE 
% ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER OR CONTRIBUTORS BE 
% LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR 
% CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF 
% SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS 
% INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN 
% CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) 
% ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE 
% POSSIBILITY OF SUCH DAMAGE.

@@

The two traffic modes, injection rate or batch, can be set by the integer paramter \texttt[use\_read\_write], where 0 means injection mode. Injection mode is on by default.

\subsubsection{Injection mode}
The rate at which packkets are injected into the simulator is set using
the \texttt{injection\_rate} option.  The simulator's cycle time is a
flit cycle, the time it takes a single flit to be injected at a
source, and the injection rate is specified in packets per flit cycle.
For example, setting \texttt{injection\_rate = 0.25} means that each
source injects a new packet one of every four simulator cycles.  The
injection process can also be specified as either Bernoulli
(\texttt{injection\_process = bernoulli}) or an on-off process
(\texttt{injection\_process = on\_off}).  The burstiness of the latter
injection process is controlled via the \texttt{burst\_alpha} and
\texttt{burst\_beta} parameter.  See PPIN Section 24.2.2 for a
description of the on-off process and its parameters.

The unit of injection is packets, which may be comprised of many

flits. All packets in injection mode are identical. The number of flits per packet is set using the
\texttt{const\_flits\_per\_packet} option.

\subsubsection{Batch mode}
Batch mode is enabled by setting \texttt{use\_read\_write= 1}. In batch mode, \texttt[injection\_rate] paramter is ignored. Instead, traffic are injected into the network as fast as possible until \texttt{batch\_size} of request packets are generated by each node. When a destination node receives a request packet, it returns a reply packet. The total number of packets injected in batch mode is 2$\times$ \texttt{batch\_size} per node. The parameter \texttt[max\_outstanding] specifies the maximum number of (request or reply) packets waiting at a node to be injected into the network.

\subsubsection{Traffic Patterns}
The simulator also supports several different traffic patterns that
are specified using the \texttt{traffic} option.  To describe these
patterns, we use the same notation of PPIN Section 3.2: $s_i$ ($d_i$)
denotes the $i^\textrm{th}$ bit of the source (destination) address
whereas $s_x$ ($d_x$) denotes the $x^\textrm{th}$ radix-$k$ digit of
the source (destination) address.  The bit length of an address is $b
= \log_2 N$, where $N$ is the number of nodes in the network.

\begin{opt_list}{trafficpatterns}
\item[uniform] Each source sends an equal amount of traffic to each
destination (\texttt{traffic = uniform}).
\item[bitcomp] Bit complement. $d_i = \neg s_i$.
\item[bitrev] Bit reverse. $d_i = s_{b-i-1}$.
\item[shuffle] $d_i = s_{i-1 \mod b}$.
\item[transpose] $d_i = s_{i+b/2 \mod b}$.
\item[tornado] $d_x = s_x + \lceil k/2 \rceil - 1 \mod k$.
\item[neighbor] $d_x = s_x + 1 \mod k$.
\item[randperm] Random permutation.  A fixed permutation traffic
pattern is chosen uniformly at random from the set of all
permutations.  The seed used to generate this permutation is set by
the \texttt{perm\_seed} option.  So, randomly selecting values for
\texttt{perm\_seed} gives a random sampling of permutation while a
fixed value of \texttt{perm\_seed} allows the same permutation to be
used for several experiments.
\end{opt_list}

>>>>

% Copyright (c) 2007-2009, Trustees of The Leland Stanford Junior University
% All rights reserved.
% 
% Redistribution and use in source and binary forms, with or without 
% modification, are permitted provided that the following conditions are met:
% 
% Redistributions of source code must retain the above copyright notice, this 
% list of conditions and the following disclaimer.
% Redistributions in binary form must reproduce the above copyright notice, 
% this list of conditions and the following disclaimer in the documentation 
% and/or other materials provided with the distribution.
% Neither the name of the Stanford University nor the names of its contributors
% may be used to endorse or promote products derived from this software without
% specific prior written permission.
% 
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" 
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE 
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE 
% ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER OR CONTRIBUTORS BE 
% LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR 
% CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF 
% SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS 
% INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN 
% CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) 
% ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE 
% POSSIBILITY OF SUCH DAMAGE.

@@

\subsubsection{Injection mode}
The rate at which packets are injected into the simulator is set using
the \texttt{injection\_rate} option.  The simulator's cycle time is a
flit cycle, the time it takes a single flit to be injected at a
source, and the injection rate is specified in packets per flit cycle\footnote{The unit of \texttt{injection\_rate} can be changed to flits per cycle by setting \texttt{injection\_rate\_uses\_flits} to 1.}.
For example, setting \texttt{injection\_rate = 0.25} means that each
source injects a new packet in one out of every four simulator cycles.

The injection process can further be specified as either Bernoulli process 
(\texttt{injection\_process = bernoulli}) or an on-off process
(\texttt{injection\_process = on\_off}).  The burstiness of the latter
is controlled via the \texttt{burst\_alpha} and
\texttt{burst\_beta} parameters.  See PPIN Section 24.2.2 for a
description of the on-off process and its parameters.

\subsubsection{Request-reply traffic}
By default, all packets that are injected into the network have the same, 
fixed length. The number of flits per packet is set using the
\texttt{const\_flits\_per\_packet} option.

Alternatively, the simulator can be configured to generate request-reply traffic. In this mode, the traffic manager injects read and write requests into the network; when a destination node receives such a request packet, it returns a reply packet of the same type\footnote{Injection of reply packets has priority over injection of new requests packets.}. Consequently, the effective overall network load is generated by both the injected requests and the automatically generated replies. Request-reply traffic ignores the \texttt{const\_flits\_per\_packet} option; instead, packet sizes are determined by the \texttt{\{read|write\}\_\{request|reply\}\_size} options. Furthermore, the mapping of packet types to VCs can be customized using the \texttt{\{read|write\}\_\{request|reply\}\_\{begin|end\}\_vc} options.

\subsubsection{Traffic patterns}
The simulator also supports several different traffic patterns that
are specified using the \texttt{traffic} option.  To describe these
patterns, we use the same notation of PPIN Section 3.2: $s_i$ ($d_i$)
denotes the $i^\textrm{th}$ bit of the source (destination) address
whereas $s_x$ ($d_x$) denotes the $x^\textrm{th}$ radix-$k$ digit of
the source (destination) address.  The bit length of an address is $b
= \log_2 N$, where $N$ is the number of nodes in the network.

\begin{opt_list}{trafficpatterns}
\item[uniform] Each source sends an equal amount of traffic to each
destination (\texttt{traffic = uniform}).
\item[bitcomp] Bit complement. $d_i = \neg s_i$.
\item[bitrev] Bit reverse. $d_i = s_{b-i-1}$.
\item[shuffle] $d_i = s_{i-1 \mod b}$.
\item[transpose] $d_i = s_{i+b/2 \mod b}$.
\item[tornado] $d_x = s_x + \lceil k/2 \rceil - 1 \mod k$.
\item[neighbor] $d_x = s_x + 1 \mod k$.
\item[randperm] Random permutation.  A fixed permutation traffic
pattern is chosen uniformly at random from the set of all
permutations.  The seed used to generate this permutation is set by
the \texttt{perm\_seed} option.  So, randomly selecting values for
\texttt{perm\_seed} gives a random sampling of permutations while a
fixed value of \texttt{perm\_seed} allows the same permutation to be
used for several experiments.
\end{opt_list}
